### 2019-05-01 README.Rmd
appveyor_check
pack_site

@@

@@

>>>>

```{r rmd-setup, include = FALSE}
knitr::opts_chunk$set(fig.path = "man/figures/")
```

@@

[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/kauedesousa/gosset?branch=master&svg=true)](https://ci.appveyor.com/project/kauedesousa/gosset)

Package website: https://kauedesousa.github.io/gosset/

@@

## Going further

The full functionality of **gosset** is illustrated in the package vignette. The vignette can be found on the [package website](https://kauedesousa.github.io/gosset/) or from within R once the package has been installed.
